---
title: "Find Context"
runtime: shiny
output: 
html_document: 
fig_caption: yes
---

- This program allows you to find utterances that match some criteria.  Then you click on a particular utterance and it will show you the file that it appears in, which allows you to see the context around the utterance.  Scroll down to the bottom for more information.  Click [here](../) to return to toolkit page.

```{r setup, include=FALSE}
library(shinycssloaders)
require(ggplot2)

ignore = "-----"
```

```{r, echo=FALSE}

shinyApp(
  ui =  fluidPage(
       tags$script(HTML("window.ga=window.ga||function(){(ga.q=ga.q||[]).push(arguments)};ga.l=+new Date;
ga('create', 'UA-7929639-6', 'auto');
ga('set', 'contentGroup1', 'filterCombine'); 
ga('send', 'pageview');")),
    tags$script(src='https://www.google-analytics.com/analytics.js'),

    sidebarPanel(selectInput("langGroup", "Language Group: ", 
                             choices = c("Eng-UK"), width='90%')
                 ,selectInput("lang", "Language: ", 
                              choices = c("Thomas"),width='90%')
                 ,selectInput("corpus", "Corpus: ", 
                              choices = c(ignore),width='90%')
                 ,selectInput("rowunit", "Row Unit:", 
                              choices = c("Word","Utterance"), selected="Utterance",width='90%')
                 ,selectInput("maxsize", "Max Size: ", 
                              choices = c(1000,10000,100000,1000000,10000000,1000000000000),width='90%',selected=1000)
                 ,textInput("search1", "Find:", "shall")
                 ,selectInput("col1", "Column: ", choices=c(ignore), width='100%')
                 ,actionButton("gotorow", "Goto Row")
                 ,width = 3)
    ,mainPanel(withSpinner(DT::dataTableOutput("table", height = '600px')))
    ,fluidRow(column(11,h4("Context")))
    ,verbatimTextOutput("debug")
    ,withSpinner(DT::dataTableOutput("results", width='800px',height = '400px'))
     ),
  server = function(input, output, session) {
    source('../childes2csv/shared3.R', local=TRUE)
    values$updateFilter = TRUE
    values$recodeUI = NULL
    values$maxsize = 1000
    values$load = TRUE
    values$forcepush=FALSE
    values$matchrows=c(1)
    values$pagelen = 20
    values$debug = "start"
 #   values$fulltable<-preread
    dd <- readFileDir("Eng-UK","Thomas",ignore)

   output$results <- DT::renderDataTable(DT::datatable(values$results,options = list(pageLength = values$pagelen,lengthMenu = c(10,20,50, 100, 1000))))
  
    output$debug <- renderPrint({ values$debug })
  
    observeEvent(input$corpus,  ignoreInit=T,{
         searchForCorpusFile() 
    })
    
     proxy = DT::dataTableProxy('results',session = session)
 
    observeEvent(input$table_rows_selected,ignoreInit=T,{
        onerow=values$table[input$table_rows_selected,]
        values$results = values$fulltable[values$fulltable$file == onerow$file,]
       values$matchrows = which(values$results[,input$col1]==onerow[,input$col1])
    #   print(values$matchrows)
        DT::selectRows(proxy, values$matchrows)
        pg = floor(first(values$matchrows-1)/values$pagelen)+1
        values$debug <- paste("gotorow ",pg)
        DT::selectPage(proxy, pg)
    })
    
    observeEvent(input$gotorow,ignoreInit=T,{
    pg = floor(first(values$matchrows-1)/values$pagelen)+1
    values$debug <- paste("gotorow ",pg)
    DT::selectPage(proxy, pg)
  })
     
     observeEvent(input$maxsize,  ignoreInit=T,{
       if (values$load){
        searchForCorpusFile()
       }
       values$load=TRUE
     })
     
     resetTable <- function(){
    if (!"ONE" %in% names(values$table) ){
      values$table$ONE = 1
    }
    cho = c(ignore,names( values$table))
    updateSelectInput(session, "col1", choices = cho,selected=ignore)
  }
  
      observeEvent(input$rowunit,{
        if (values$load){
        searchForCorpusFile()
        resetTable()
        }
        values$load=TRUE
     })
      
    
    observe({
      #      input$search1
      #      input$search2
      #      input$search3
      input$col1
 #     print("observe")
      isolate({
        values$table <- values$fulltable
        values$debug <-"searching"
      
        if (input$col1 %in% names(values$table) ){
          values$table[,input$col1]=as.character(values$table[,input$col1])
          check = str_detect(values$table[,input$col1],input$search1)
          values$debug <- sum(check)
 #         values$table = values$table[!is.na(values$table[,input$col1]) && check,]
          values$table <- values$table[check,]
          #c("role",input$col1,"file", "corpus","langgrp","uID")]
          #"langtype",
        }
      })
    })
    
    roundTwo <- function(x){
      i = 1
      while(round(x,i) == 0){
        i = i+1
      }
      return(round(x,i+1))
    }

    output$downloadDataResults <- downloadHandler(
      filename = function() { 
        paste(input$langGroup,",",input$lang,",",input$corpus,"_",input$rowunit,"Counts.csv",sep="")
      },
      content <- function(file) {
        write.csv(values$results, file =file,fileEncoding = "UTF-8",quote=T)
      }
      ,contentType = "text/csv"
    )
    
    output$downloadFilter <- downloadHandler(
      filename = function() { 
        paste(input$langGroup,",",input$lang,",",input$corpus,"_",input$rowunit,"Filtered.csv",sep="")
      },
      content <- function(file) {
        values$table$REGEXPTERM = paste(input$col1,"=",input$search1,";",input$col2,"=",input$search2,";",input$col3,"=",input$search3,";",sep="")
        write.csv(values$table, file =file,fileEncoding = "UTF-8",quote=T,row.names = F)
      }
      ,contentType = "text/csv"
    )
  }
  ,options = list(width=1000,height = 1200)
)
```

- This program allows you to find particular words/utterances in CHILDES corpora and then see the context around those utterances to better understand how they are used.  You first select the language group, language, corpus, and row unit that you want to use.  Max size determines the maximum size of the corpus (the server is too slow for some analyses when using the whole corpus).
- In the Find box, put a regular expression that you want to search for.  You can search for dog by putting dog in the box.  Then you need to select the column that you want to search.  Normally, you would select w to search the words/utterances.  The data frame on the right top will update to show the items that match your search.
- If you find an item that you want to see the context for, just click on that row in the table and a new table will appear below showing the file that the utterance comes from.
- To learn more about regular expressions, look [here](https://regexone.com/lesson/introduction_abcs).  
- You can download the results or the original table using the download buttons.
- These tools are still a work in progress and you should check any results with the original CHILDES corpora.  
- This work is part of the toolkit project within the ESRC International Centre for Language and Communicative Development (LuCiD) (http://www.lucid.ac.uk/, ESRC grant [ES/L008955/1]).  Please contact [Franklin Chang](https://sites.google.com/site/sentenceproductionmodel/cv) with any questions.
- To cite these tools, please use this reference: Chang, F. (2017) The LuCiD language researcher's toolkit [Computer software]. Retrieved from http://www.lucid.ac.uk/resources/for-researchers/toolkit/


