---
title: "Find Context"
runtime: shiny
output: 
html_document: 
fig_caption: yes
---

- This program allows you to find utterances that match some criteria and then check what they mean in context.
- Type a regular expression in the find box and select the column that you want to search (to try it out, go to the Column selector and choose w).
- You should see the matching utterances in the Find Table on the top right
- Select an utterance and you should see the whole file that it appeared in below in the Context Table
- The row with the target utterance should be highlighted (click again if it doesn't show up)
- Scroll down to the bottom for more information.  Click [here](../) to return to toolkit page.

```{r setup, include=FALSE}
library(shinycssloaders)
require(ggplot2)

ignore = "-----"
```

```{r, echo=FALSE}

ui <-  fluidPage(
  tags$script(HTML("window.ga=window.ga||function(){(ga.q=ga.q||[]).push(arguments)};ga.l=+new Date;
ga('create', 'UA-7929639-6', 'auto');
ga('set', 'contentGroup1', 'findContext'); 
ga('send', 'pageview');")),
tags$script(src='https://www.google-analytics.com/analytics.js'),

sidebarPanel(selectInput("langGroup", "Language Group: ", 
                         choices = c("Eng-UK"), width='90%')
             ,selectInput("lang", "Language: ", 
                          choices = c("Thomas"),width='90%')
             ,selectInput("corpus", "Corpus: ", 
                          choices = c(ignore),width='90%')
             ,selectInput("rowunit", "Row Unit:", 
                          choices = c("Word","Utterance"), selected="Utterance",width='90%')
             ,selectInput("maxsize", "Max Size: ", 
                          choices = c(1000,10000,100000,1000000,10000000,1000000000000),width='90%',selected=1000)
             ,textInput("search1", "Find:", "shall.+?put")
             ,selectInput("col1", "Column: ", choices=c(ignore), width='100%')
            # ,actionButton("gotorow", "Goto Row")
             ,width = 3)
,mainPanel(fluidRow(column(11,h4("Find Table")))
,withSpinner(DT::dataTableOutput("table", height = '600px')))
,fluidRow(column(11,h4("Context Table")))
,withSpinner(DT::dataTableOutput("results", width='800px',height = '400px'))
,verbatimTextOutput("debug")
)

server <- function(input, output, session) {
  source('../childes2csv/shared3.R', local=TRUE)
  values$updateFilter = TRUE
  values$recodeUI = NULL
  values$maxsize = 1000
  values$load = TRUE
  values$forcepush=FALSE
  values$matchrows=c(1)
  values$pagelen = 10
  values$debug = ""
  values$results = NULL
  values$resultlongcol = c()
  #   values$fulltable<-preread
  dd <- readFileDir("Eng-UK","Thomas",ignore)
  
  proxy = DT::dataTableProxy('results', session = session)
  
  output$results <- DT::renderDataTable(DT::datatable(values$results
                            ,options = list(searching = FALSE,autoWidth = TRUE,processing = TRUE,
                                           pageLength = values$pagelen,lengthMenu = c(10,20,50, 100, 1000)
                                          ,columnDefs = list(list(width = '1000px', targets = values$resultlongcol))
                                           )  ),server = TRUE)

  output$debug <- renderPrint({ values$debug })
  
  observeEvent(input$corpus,  ignoreInit=T,{
    searchForCorpusFile() 
    updateFindTable()
  })
    
  selectFile <- function() {
    onerow = values$table[input$table_rows_selected, ]
    values$results = values$fulltable[values$fulltable$file == onerow$file, ]
    
    if (input$col1 != ignore) {
        values$matchrows <-
          which(values$results[, input$col1] == onerow[, input$col1])
      } else{
        values$matchrows <- which(values$results$w == onerow$w)
      }
      
  }
  
  formatResultTable <- function(){
    if (!is.null(values$results )){
      if (nrow(values$results) > 4) {
        print("adjust rescol")
        vdf1 = values$results
        head(vdf1)
        if (length(vdf1[, 1]) > 1000) {
          vdf1 = values$results[1:1000, ]
        }
        collength = data.frame(apply(apply(vdf1, 1, nchar), 1, max))
        #    print(unique(vdf$t_type))
        print(collength)
        if ("rowunit" %in% input && input$rowunit == "Utterance") {
          values$resultlongcol = union(which(names(vdf1) == "w"), which(collength > 40))
          # values$text = paste(values$longcol)
        } else{
          # word
          values$resultlongcol = which(collength > 12)
        }
        print(values$resultlongcol)
      }
      
      
      #   print(values$matchrows)
      #  values$debug <- paste(values$matchrows)
      DT::selectRows(proxy, values$matchrows)
      if (length(values$matchrows) > 0) {
        values$pagelen <- length(input$results_rows_current)
        pg = floor(first(values$matchrows - 1) / values$pagelen) + 1
        #   values$debug <- paste("gotorow ",pg)
        DT::selectPage(proxy, pg)
      }
    }
  }
  
  #    session$onFlushed(function() {
  #      if (length(values$results) > 1){
  #        values$debug <- "results set"
  #      }
  #    })
  
  observeEvent(input$table_rows_selected, ignoreInit = T, {
    selectFile()
  })
  
  observe({
    invalidateLater(2000)
  
    values$results
    isolate({
       formatResultTable()
    })
  })
  
  observeEvent(input$maxsize,  ignoreInit=T,{
    if (values$load){
      searchForCorpusFile()
    }
    values$load=TRUE
  })
  
  resetTable <- function(){
    if (!"ONE" %in% names(values$table) ){
      values$table$ONE = 1
    }
    cho = c(ignore,names( values$table))
    updateSelectInput(session, "col1", choices = cho,selected=ignore)
  }
  
  observeEvent(input$rowunit,{
    if (values$load){
      searchForCorpusFile()
      resetTable()
      updateFindTable()
      values$debug <- ""
    }
    values$load=TRUE
  })
  
  updateFindTable <- function(){
    isolate({
       if (input$col1 %in% names(values$fulltable) ){
        values$table <- values$fulltable
        col1=as.character(values$table[,input$col1])
        check =  str_detect(col1,input$search1)
    #    values$debug <- sum(check)
        #         values$table <- values$table[!is.na(values$table[,input$col1]) && check,]
        newname = c(c("file",input$col1),setdiff(names(values$table),c("file",input$col1)))
       # values$debug = newname
        values$table <- values$table[check,]
        values$table <- values$table[newname]
        
        #c("role",input$col1,"file", "corpus","langgrp","uID")]
        #"langtype",
      }
    })
  }
  
  observe({
    #      input$search1
    #      input$search2
    #      input$search3
    input$col1
    #     print("observe")
    updateFindTable()
  })
  
  observe({
    values$table
     adjustTableCol()
  })
  
  roundTwo <- function(x){
    i = 1
    while(round(x,i) == 0){
      i = i+1
    }
    return(round(x,i+1))
  }
  
  output$downloadDataResults <- downloadHandler(
    filename = function() { 
      paste(input$langGroup,",",input$lang,",",input$corpus,"_",input$rowunit,"Counts.csv",sep="")
    },
    content <- function(file) {
      write.csv(values$results, file =file,fileEncoding = "UTF-8",quote=T)
    }
    ,contentType = "text/csv"
  )
  
  output$downloadFilter <- downloadHandler(
    filename = function() { 
      paste(input$langGroup,",",input$lang,",",input$corpus,"_",input$rowunit,"Filtered.csv",sep="")
    },
    content <- function(file) {
      values$table$REGEXPTERM = paste(input$col1,"=",input$search1,";",input$col2,"=",input$search2,";",input$col3,"=",input$search3,";",sep="")
      write.csv(values$table, file =file,fileEncoding = "UTF-8",quote=T,row.names = F)
    }
    ,contentType = "text/csv"
  )
}


shinyApp(ui = ui, server = server ,options = list(width=1000,height = 1200))

```

- This program allows you to find particular words/utterances in CHILDES corpora and then see the context around those utterances to better understand how they are used.  You first select the language group, language, corpus, and row unit that you want to use.  Max size determines the maximum size of the corpus (the server is too slow for some analyses when using the whole corpus).
- In the Find box, put a regular expression that you want to search for.  To search for "shall" followed by "put", just type shall.+?put in the box. Then you need to select the column that you want to search.  Normally, you would select w to search the words/utterances.  The data frame on the right top will update to show the items that match your search.
- If you find an item that you want to see the context for, just click on that row in the Find Table and a new Context Table will appear below showing the file that the utterance comes from.  You should see the row with your item highlighted, but if it doesn't work, please click on the row again in the Find Table.
- To learn more about regular expressions, look [here](https://regexone.com/lesson/introduction_abcs).  
- These tools are still a work in progress and you should check any results with the original CHILDES corpora.  
- This work is part of the toolkit project within the ESRC International Centre for Language and Communicative Development (LuCiD) (http://www.lucid.ac.uk/, ESRC grant [ES/L008955/1]).  Please contact [Franklin Chang](https://sites.google.com/site/sentenceproductionmodel/cv) with any questions.
- To cite these tools, please use this reference: Chang, F. (2017) The LuCiD language researcher's toolkit [Computer software]. Retrieved from http://www.lucid.ac.uk/resources/for-researchers/toolkit/


