---
title: "Childes Generator"
runtime: shiny
output: 
html_document: 
fig_caption: yes
---

- Generate Word Sequences using ngrams from CHILDES Corpora.  Click [here](../) to return to toolkit page.
- You can select the language group, language, and corpora (these are based on the directory structure in CHILDES)
- Then select whether you want them for the target child or all other speakers (mostly the parents)
- Use the checkboxes to select the next word in the sentence.
- Transitional probabilities for the last word based on the previous context are shown. The choices are ordered by probabilities, so the top choice is the most likely continuation.  You will see a selection of some high probability, middle probability, and low probability items.
- The reset button will remove the sentence and it will show you some unigrams from the corpus.  You can also type your own words in the textbox.
- If you do not select a particular language or corpus, you will get all of the ngrams from all of the corpora under that language group or language. 
```{r setup, include=FALSE}
library(shinycssloaders)
require(ggplot2)
ignore = "-----"

ngramdir = "../storage/ngrams"


```

```{r, echo=FALSE}

shinyApp(
  ui =  fluidPage(
    tags$script(HTML("window.ga=window.ga||function(){(ga.q=ga.q||[]).push(arguments)};ga.l=+new Date;
ga('create', 'UA-7929639-6', 'auto');
ga('set', 'contentGroup1', 'childesgen'); 
ga('send', 'pageview');")),
tags$script(src='https://www.google-analytics.com/analytics.js'),
fluidRow(column(3,selectInput("langGroup", "Language Group: ", 
                              choices = c("Eng-UK"), width='90%'))
         ,column(3,selectInput("lang", "Language: ",
                               choices = c("Thomas"),width='90%'))
         ,column(3,selectInput("corpus", "Corpus: ", 
                               choices = c("-----"),width='90%'))
         ,column(3,selectInput("speaker", "Speaker", 
                              choices = c("Target_Child","Others"), selected="Others",width='90%'))        
         ,column(1,actionButton("reset", "Reset"),br(),br(),actionButton("back", "Back")))
,fluidRow(column(10,textInput('wordseq',"Word Sequence","I want",width='1400px')))
,fluidRow(column(10,textOutput("bigram"),textOutput("trigram")))
,fluidRow(column(10,checkboxGroupInput("selectnextword", label = "Select the next word")))
  ),
server = function(input, output, session) {
  source('../childes2csv/shared3.R', local=TRUE)
  values$updateFilter = TRUE
  values$changeSearch = FALSE
  values$addignore=TRUE
  values$n1 = "NULL"
  values$n2 = "NULL"
  values$n3 = "NULL"
  values$n4 = "NULL"
  values$bigram= ""
  values$trigram = ""
  values$wordseq = c("I","want")
  dd <- readFileDir("Eng-UK","Thomas","-----",addignore=TRUE)
  
  output$bigram <- renderText({ values$bigram })
  output$trigram <- renderText({ values$trigram })
  #  output$value <- renderText({ input$caption })
  
  observeEvent(input$corpus,ignoreInit=T, {
    values$n1 = "NULL"
    values$n2 = "NULL"
    values$n3 = "NULL"
    values$n4 = "NULL"
    values$bigram= ""
    values$trigram = ""
    #       updateTextInput(session, "wordseq", value = "")
            updateSelection()
  })
  
  observeEvent(input$lang, ignoreInit=T,{
    values$n1 = "NULL"
    values$n2 = "NULL"
    values$n3 = "NULL"
    values$n4 = "NULL"
    values$bigram= ""
    values$trigram = ""
    #     updateTextInput(session, "wordseq", value = "")
          updateSelection()
  })
  
  observeEvent(input$speaker, ignoreInit=T,{
    values$n1 = "NULL"
    values$n2 = "NULL"
    values$n3 = "NULL"
    values$n4 = "NULL"
    values$bigram= ""
    values$trigram = ""
    updateSelection()
  })
  
  observeEvent(input$reset, {
    print("reset")
    isolate({
      updateTextInput(session, "wordseq", value = "")
      values$wordseq= c()
      #  values$wordseq=c()
    })
    updateSelection()
  })
  
  observeEvent(input$back, {
    print("back")
    isolate({
      values$wordseq=values$wordseq[1:(length(values$wordseq)-1)]
      updateTextInput(session, "wordseq", value = paste(values$wordseq,collapse=" "))
      values$wordseq= c()
      #  values$wordseq=c()
    })
    updateSelection()
  })
  
  observeEvent(input$selectnextword,{
    values$wordseq=c(values$wordseq,input$selectnextword)
    newstr = paste(values$wordseq,collapse = " ")
    newstr = str_replace(newstr,"#ppp",".")
    newstr = str_replace(newstr,"#qqq","?")
    updateTextInput(session, "wordseq", value = newstr)
  })
  
  getNgrams <- function(num){
    if (num == 1){
      if (!is.data.frame(values$n1)){
        values$n1 = loadCorpora("1")
      }
      return(values$n1)
    }
    if (num == 2){
      if (!is.data.frame(values$n2)){
        values$n2 = loadCorpora("2")
      }
      return(values$n2)
    }
    if (num == 3){
      if (!is.data.frame(values$n3)){
        values$n3 = loadCorpora("3")
      }
      return(values$n3)
    }
    if (num == 4){
      if (!is.data.frame(values$n4)){
        values$n4 = loadCorpora("4")
      }
      return(values$n4)
    }
    return(NULL)
  }
  
  observeEvent(values$wordseq,{
    print("values")
    n1 = getNgrams(1)
    #    wordseq = c("I","want","to","buy")
    wordseq = values$wordseq
    # print(head(n1))
    plus = paste(wordseq," ",sep="")
    stat = n1[match(plus,n1$ngrams),]
    
    if (length(wordseq) > 1){
      tdf = as.data.frame(t(mapply(list,wordseq[1:length(wordseq)-1], wordseq[2:length(wordseq)])))
      tdf$bi = paste(tdf$V1,tdf$V2,"")
      #     print(tdf)
      n2 = getNgrams(2)
      bigramfreq = n2$freq[match(tdf$bi,n2$ngrams)]
      prop = bigramfreq / stat$freq[1:(length(wordseq)-1)]
      stat$bigramfreq = c(NA,bigramfreq)
      stat$bigram = c(NA,prop)
      print(stat)
      bigram = stat$bigram[!is.na(stat$bigram)]
      values$bigram = paste("Bigram probabilities",paste(signif(bigram),collapse=" * "),"=", signif(prod(bigram, na.rm=F)))
    }
    
    if (length(wordseq) > 2){
      tdf = as.data.frame(t(mapply(list,wordseq[1:(length(wordseq)-2)],wordseq[2:(length(wordseq)-1)], wordseq[3:length(wordseq)] )))
      tdf$tri = paste(tdf$V1,tdf$V2,tdf$V3,"")
      print(tdf)
      n3 = getNgrams(3)
      print(head(n3))
      #      print(n2$freq[n2$ngrams %in% tdf$bi])
      prop = n3$freq[match(tdf$tri,n3$ngrams)] / stat$bigramfreq[2:(length(wordseq)-1)]
      stat$trigram = c(NA,NA,prop)
      print(stat)
      trigram = stat$bigram[!is.na(stat$trigram)]
      values$trigram = paste("Trigram probabilities",paste(signif(trigram),collapse=" * "),"=", signif(prod(trigram, na.rm=F)))
    }
  })
  
  observeEvent(input$wordseq,{
    updateSelection()
  })
  
  updateSelection <- function(){
    values$wordseq=strsplit(input$wordseq," ")[[1]]
    seqlen = length(values$wordseq)
    bot = 1
    if (seqlen > 3){
      bot = seqlen - 2
    }
    contextseq = values$wordseq[bot:seqlen]
    contextseq = str_replace(contextseq,"[.]", "#ppp")
    contextseq = str_replace(contextseq,"[?]", "#qqq")
    context = paste(contextseq,collapse=" ")
    print(context)
    contlen = length(contextseq)
    
    ngramsmall = getNgrams(contlen)
    #   print(n2freq)
    ngramfull = getNgrams(contlen+1)
    if (is.null(ngramsmall) || is.null(ngramfull)){
      updateCheckboxGroupInput(session, "selectnextword",choices = character(0) )
    }else{
    #    print(head(ngramfull))
    #   paste(values$wordseq,collapse=" ")
    df2 = subset(ngramfull,str_detect(ngramfull$ngrams,paste("^",context," .*",sep="")))
    #     print(dim(df2))
    if (is.data.frame(df2) && nrow(df2)>0){
      n2freq = ngramsmall$freq[ngramsmall$ngrams==paste(context," ",sep="")]
      df2 = df2[order(-df2$freq),]
      lendf2 = length(df2$freq)
      df2$final = str_match(df2$ngrams,paste("^",context," ([^ ]+)",sep=""))[,2]
      #      print(lendf2)
      #      print(head(df2))
      
      df3 = df2
      #        }
      #  print("df3")
      #  print(df3)
      if (length(n2freq) > 0){
        df3$prop = signif(df3$freq / n2freq)
      }else{
        df3$prop = df3$freq
      }
      df3$label = paste("\"",df3$ngrams," ",df3$prop,"\"=\"",df3$final,"\"",sep="")
      #          print(df3$label)
      newstr = paste("list(",paste(df3$label,collapse=","),")")
      newstr = str_replace(newstr,"#ppp",".")
      newstr = str_replace(newstr,"#qqq","?")
      #    print(newstr)
      listparse = eval(parse(text=newstr))
      #    print(listparse)
      updateCheckboxGroupInput(session, "selectnextword",choices = listparse )
    }else{
      print("empty")
      updateCheckboxGroupInput(session, "selectnextword",choices =character(0) )
    }
    if (input$wordseq==""){
      ngramfull = getNgrams(1)
      uniqval = unique(ngramfull$freq)
      med = uniqval[length(uniqval)/2]
      #  print(med)
      mid = which(ngramfull$freq==med)
      # print(mid)
      s = 4
      lendf2=length(ngramfull$freq)
      df3 = ngramfull[c(1:2*s, (mid-s):(mid+s), (lendf2-2*s+1):lendf2),]
      df3$prop = df3$freq 
      df3$label = paste("\"",df3$ngrams," ",df3$prop,"\"=\"",df3$ngrams,"\"",sep="")
      #   print(head(df3))
      newstr = paste("list(",paste(df3$label,collapse=","),")")
      listparse = eval(parse(text=newstr))
      updateCheckboxGroupInput(session, "selectnextword",choices = listparse )
    }
    }
  }
  
  getFileName <- function(nopath,gram,extra=""){
    fpath = paste(ngramdir, "/",input$langGroup,"_",input$lang,"_",input$corpus, "_",gram,extra,".rds",sep="")
    if (input$lang == ignore | input$lang == ""){
      fpath = paste(ngramdir, "/",input$langGroup,"_",gram,extra,".rds",sep="")
    }else{
      if (input$corpus == ignore | input$corpus == ""){
        fpath = paste(ngramdir, "/",input$langGroup,"_",input$lang,"_",gram,extra,".rds",sep="")
      }
    }
    if (nopath){
      fpath = str_replace(fpath,paste(ngramdir,"/",sep=""),"")
    }
    print(fpath)
    return(fpath)
  }
  
  loadCorpora <- function(gram){
    fpath = getFileName(FALSE,gram,paste("_",input$speaker,sep=""))
    print(fpath)
    if (file.exists(fpath)){
      print(paste("found",fpath))
      df = readRDS(fpath)
      # df = df[order(df$ngrams),]
      return(df)
    }
    return(NULL)
  }
  
  output$logrank<-renderPlot({
    if (length(values$table) > 2 & "rank" %in% names(values$table)){
      ngdf = values$table
      ngdf = ngdf[ngdf$punct == 0,]
      ggplot(ngdf,aes(x=logrank,y=logfreq))+geom_point(colour='red')+stat_smooth(method="lm")
    }
  })
  
  output$downloadNgram <- downloadHandler(
    filename = function() { 
      ff= getFileName(TRUE)
      ff=sub(".rds",".csv",ff)
      ff
    },
    content <- function(file) {
      fpath = getFileName(FALSE)
      print(fpath)
      wholecsv <- readRDS(fpath)
      write.csv(wholecsv, file)
      
    }
    ,contentType = "text/csv"
  )
}
,options = list(width=1000,height = 560)
)
```

- The transitional probabilities are computed by taking the frequency of the last three words and dividing by the frequency of the bigram composed of the first two words within the trigram.  For the utterance "I want a drink", the frequency of "want a drink" will be divided by the frequency of "want a".  This tells us out of all of the cases of "want a", what proportion were followed by "drink".  If the sequence is only two words, then bigram frequency is divided by the unigram frequency of the first word.

- The first few clicks will be slow to update, because files need to be loaded.

- These tools are still a work in progress and you should check any results with the original CHILDES corpora.  

- This work is part of the toolkit project within the ESRC International Centre for Language and Communicative Development (LuCiD) (http://www.lucid.ac.uk/, ESRC grant [ES/L008955/1]).  Please contact [Franklin Chang](https://sites.google.com/site/sentenceproductionmodel/cv) with any questions.
- To cite these tools, please use this reference: Chang, F. (2017) The LuCiD language researcher’s toolkit [Computer software]. Retrieved from http://gandalf.talkbank.org:8080/
