---
title: "Filter Recode Combine CHILDES Analyses"
runtime: shiny
output: 
html_document: 
fig_caption: yes
---

- This program allows you to do some simple analyses with CHILDES corpora.  You can filter for some target items, recode some columns into numeric values, and then group those values and report some combined metric for those values.  Scroll down to the bottom for more information.  Click [here](../) to return to toolkit page.

```{r setup, include=FALSE}
library(shinycssloaders)

ignore = "-----"
preread <- read.csv("../storage/actualcsv/Eng-UK_Belfast_Barbara_Word.csv",nrows=1000)
```

```{r, echo=FALSE}

shinyApp(
  ui =  fluidPage(
    sidebarPanel(selectInput("langGroup", "Language Group: ", 
                             choices = c("Eng-UK"), width='90%')
                 ,selectInput("lang", "Language: ", 
                              choices = c("Belfast"),width='90%')
                 ,selectInput("corpus", "Corpus: ", 
                              choices = c("Barbara"),width='90%')
                 ,selectInput("rowunit", "Row Unit:", 
                              choices = c("Word","Utterance"), selected="Word",width='90%')
                 ,selectInput("maxsize", "Max Size: ", 
                              choices = c(1000,10000,100000,1000000,10000000,1000000000000),width='90%')
                 ,width = 3)
    ,mainPanel(withSpinner(DT::dataTableOutput("table", height = '400px')))
    ,fluidRow(column(8,h4("Filter: Put a search string in the expression box and then selecting a column to filter on.  Strings and regular expressions are acceptable.")), column(3, downloadButton('downloadFilter','Download Filtered')))
 #   ,tags$td("")
      ,fluidRow(
        column(3 ,textInput("search1", "Expression1:", "^(this|that)$")
               ,selectInput("col1", "Column1: ", choices=c(ignore), width='100%'))
        ,column(3,textInput("search2", "Expression2:", "Target_Child"), 
                selectInput("col2", "Column2: ", choices=c(ignore),width='100%'))
        ,column(3,textInput("search3", "Expression3:", "[A-z]+?ed$"), 
                selectInput("col3", "Column3: ", choices=c(ignore),width='100%'))
        ,column(2, h6("Filtered CSV")))
   ,fluidRow(column(11,h4("Recode: Create a new column where levels of one column have been converted into numbers/strings.")))
      ,fluidRow(
        column(3,selectInput("source1", "Source: ", choices=c(ignore), width='100%'),actionButton("create", "Create"))
        ,uiOutput("recodeUI"))
    ,fluidRow(column(8,h4("Combine: Compute counts or means by some grouping values")),column(3, downloadButton('downloadDataResults', 'Download Combined')))
     ,fluidRow(
        column(2, selectInput("grp1", "Group1: ", choices=c(ignore),width='100%'))
        ,column(2, selectInput("grp2", "Group2: ", choices=c(ignore),width='100%'))
        ,column(2, selectInput("grp3", "Group3: ", choices=c(ignore),width='100%'))
        ,column(2, selectInput("comb", "Combine: ", choices=c("count","mean"),selected="count", width='100%'))
        ,column(2, selectInput("dv", "DepVar: ", choices=c(ignore,"ONE"),selected="Word", width='100%'))
        ,column(2, h6("Count CSV"))
        )
     ,withSpinner(DT::dataTableOutput("results", width='800px',height = '400px'))
     ),
  server = function(input, output, session) {
    source('../childes2csv/shared3.R', local=TRUE)
    values$updateFilter = TRUE
    values$recodeUI = NULL
    values$maxsize = 1000
    values$fulltable<-preread
    dd <- readFileDir("Eng-UK","Belfast","Barbara")

    # results data at bottom
    output$results <- DT::renderDataTable(DT::datatable(values$results))
    
    resetTable <- function(){
         if (!"ONE" %in% names(values$table) ){
            values$table$ONE = 1
         }
          dv = "ONE"
          cho = c(ignore,names( values$table))
          updateSelectInput(session, "source1", choices = cho,selected=ignore)
          updateSelectInput(session, "dv", choices = cho,selected=dv)
          updateSelectInput(session, "col1", choices = cho,selected=ignore)
          updateSelectInput(session, "col2", choices = cho,selected=ignore)
          updateSelectInput(session, "col3", choices = cho,selected=ignore)
          updateSelectInput(session, "grp1", choices = cho,selected=ignore)
          updateSelectInput(session, "grp2", choices = cho,selected=ignore)
          updateSelectInput(session, "grp3", choices = cho,selected=ignore)
 
    }
    
    observeEvent(input$corpus,  ignoreInit=T,{
         searchForCorpusFile()
        resetTable()
    })
     
     observeEvent(input$maxsize,  ignoreInit=T,{
        values$maxsize = as.integer(input$maxsize)
        searchForCorpusFile()
        resetTable()
     })
     
      observeEvent(input$rowunit,{
        searchForCorpusFile()
        resetTable()
     })
     
#      
# observeEvent(values$table,{
#   if (nrow(values$table)>2){
#     dv = input$dv
#     if (!"ONE" %in% names(values$table) ){
#       values$table$ONE = 1
#       if (dv == ignore)
#       dv = "ONE"
#     }
#     cho = c(ignore,names( values$table))
#     source1=input$source1
#     updateSelectInput(session, "source1", choices = cho,selected=source1)
#     updateSelectInput(session, "dv", choices = cho,selected=dv)
#     col1 = input$col1
#     updateSelectInput(session, "col1", choices = cho,selected=col1)
#     col2 = input$col2
#     updateSelectInput(session, "col2", choices = cho,selected=col2)
#     col3 = input$col3
#     updateSelectInput(session, "col3", choices = cho,selected=col3)
#     grp1 = input$grp1
#     updateSelectInput(session, "grp1", choices = cho,selected=grp1)
#     grp2 = input$grp2
#     updateSelectInput(session, "grp2", choices = cho,selected=grp2)
#     grp3 = input$grp3
#     updateSelectInput(session, "grp3", choices = cho,selected=grp3)
#     
#   }
# })

   output$recodeUI <- renderUI(values$recodeUI)
     
   observeEvent(input$source1,  ignoreInit=T,{
      if (input$source1 %in% names(values$table)){
        lev = as.character(unique(values$table[,input$source1]))
     #   print(lev)
        level_list <- lapply(lev, function(le) {
        #  print(le)
          column(2,textInput(le, label=le, value=NA))
       })
      values$recodeUI <- do.call(tagList, level_list)
      
      updateActionButton(session,"create", label=paste("Create new_",input$source1,sep=""))

      }
    })
    
    observeEvent(input$create, ignoreInit=T,{
      print("create")
      if (input$source1 %in% names(values$table)){
        newcol = paste("new_",input$source1,sep="")
        colval = as.character(values$table[,input$source1])
        lev = as.character(unique(values$table[,input$source1]))
        print(lev)
     #   print(head(colval))
        lapply(lev, function(le) {
        #  print(le)
          column(2,textInput(le, label=le, value=NA))
       })
        
        values$table[newcol] = NA
        for (i in 1:length(lev)){
 #         print(lev[i])
          rep = input[[lev[i]]]
  #        print(rep)
   #       print(is.na(as.numeric(rep)))
    #      print(rep=="")
          if (rep==""){
            values$table[colval==lev[i],newcol] = ""
          }else{
            values$table[colval==lev[i],newcol] = rep
          }
        }
        print( values$table[newcol] )

        numcol = which(newcol == names(values$table))
        values$table = values$table[,c(numcol,setdiff(1:length(values$table), numcol))]
        updateSelectorTable()
      }
    })
    
    observe({
      #      input$search1
      #      input$search2
      #      input$search3
      input$col1
      input$col2
      input$col3
 #     print("observe")
      isolate({
        values$table <- values$fulltable
        
        if (input$col1 %in% names(values$table) ){
          values$table[,input$col1]=as.character(values$table[,input$col1])
          values$table = values$table[!is.na(values$table[,input$col1]) & str_detect(values$table[,input$col1],input$search1),]
        }
        if (input$col2 %in% names(values$table)){
          values$table[,input$col2]=as.character(values$table[,input$col2])
          values$table = values$table[!is.na(values$table[,input$col2]) & str_detect(values$table[,input$col2],input$search2),]
        }
        if (input$col3 %in% names(values$table)){
          values$table[,input$col3]=as.character(values$table[,input$col3])
          values$table = values$table[!is.na(values$table[,input$col3]) & str_detect(values$table[,input$col3],input$search3),]
        }
      })
    })
    
    observe({
      input$grp3
      input$grp2
      input$grp1
      input$comb 
      input$dv
      isolate({
      processTable=NULL
      if (!is.null(values$table) && length(values$table) > 2){
        if (!is.null(input$grp3 ) && input$grp3 %in% names(values$table) ){
          processTable =  values$table %>% group_by_( input$grp1, input$grp2, input$grp3 )
        }else{
          if (!is.null(input$grp2 ) && input$grp2 %in% names(values$table) ){
            processTable =  values$table %>% group_by_(input$grp1, input$grp2 )
          }else{
            if (!is.null(input$grp1 ) && input$grp1 %in% names(values$table) ){
              processTable =  values$table %>% group_by_(input$grp1 )
              
            }
          }
        }
        if (!is.null(processTable)){
          print("Grouping")
          print(head(values$table))
          if (input$comb == "count"){
            values$results = processTable %>% summarize(n =  n()) %>% arrange(desc(n))
          }
          if (input$comb == "mean" && input$dv %in% names(processTable)){
            print("mean")
      #      print(head(processTable[input$dv],100))
      #      processTable[input$dv]=as.numeric(as.character(processTable[input$dv]))
       #     print(head(processTable[input$dv],100))
            summ <- paste0('mean(as.numeric(as.character(', input$dv, ')), na.rm = TRUE)')  # construct summary method, e.g. mean(mpg)
            summ_name <- paste0('mean_', input$dv)  # construct summary variable name, e.g. mean_mpg
            values$results = processTable %>% summarise_(.dots = setNames(summ, summ_name))
            
            #%>% arrange(desc(n))
          }
        }
      }
      })
    })


    output$downloadDataResults <- downloadHandler(
      filename = function() { 
        paste(input$langGroup,",",input$lang,",",input$corpus,"_",input$rowunit,"Counts.csv",sep="")
      },
      content <- function(file) {
        write.csv(values$results, file =file,fileEncoding = "UTF-8",quote=T)
      }
      ,contentType = "text/csv"
    )
    
    output$downloadFilter <- downloadHandler(
      filename = function() { 
        paste(input$langGroup,",",input$lang,",",input$corpus,"_",input$rowunit,"Filtered.csv",sep="")
      },
      content <- function(file) {
        values$table$REGEXPTERM = paste(input$col1,"=",input$search1,";",input$col2,"=",input$search2,";",input$col3,"=",input$search3,";",sep="")
        write.csv(values$table, file =file,fileEncoding = "UTF-8",quote=T,row.names = F)
      }
      ,contentType = "text/csv"
    )
  }
  ,options = list(width=1000,height = 1200)
)
```

- This program filters CHILDES corpora.  You first select the language group, language, corpus, and row unit that you want to use.  Max size determines the maximum size of the corpus (the server is too slow for some analyses when using the whole corpus).
- Let's say you want to see how the words "this" and "that" are used over development.  You can put the regular expression ^(this|that)$ into the Expression1 box.  Then change Column1 to the word column, which is w.  To learn more about regular expressions, click [here](https://regexone.com/lesson/introduction_abcs).  
- Then you need to convert these words into numbers, so in the Recode section, put "w"" in the Source and you will see a set of boxes for "this" and "that".  Put a 1 in the "that" box and a 0 in the "this" box.  Then click Create and you will get a column new_w which codes 1 for "that" and 0 for "this" (see table above)
- Now we want to see how the use of "this" and "that" change over development, so we put Y in the Group1 column.  Since the DepVar is 1 and Combine is "count", you will get a count of the number of lines with either this and that for each year. Now change the Combine to "mean" and the DepVar to "new_w" and you will see the mean proportion of "that" produced. You can download the results or the original table using the download buttons.
- This work is part of the toolkit project within the ESRC International Centre for Language and Communicative Development (LuCiD) (http://www.lucid.ac.uk/, ESRC grant [ES/L008955/1]).  Please contact Franklin Chang with any questions.
- To cite these tools, please use this reference: Chang, F. (2017) The LuCiD language researcher's toolkit [Computer software]. Retrieved from http://www.lucid.ac.uk/resources/for-researchers/toolkit/

